\textbf{Rete Convoluzionale per Image Deblurring}

### 2025-06-14 docs/paper.tex
documento

% Compilation commands
% lualatex paper.tex
% makeglossaries paper
% bibtex paper
% lualatex paper.tex

@@

% glossary
\usepackage[acronym, toc]{glossaries}
\makeglossaries
\usepackage[backend=bibtex, style=numeric]{biblatex}
\addbibresource{references.bib}

@@

@@

% \begin{figure}[h]\begin{mdframed}[
%       linewidth=1pt,
%       innertopmargin=6pt,
%       innerbottommargin=6pt,
%       innerleftmargin=6pt,
%       innerrightmargin=6pt
%       linecolor=black,
%       nobreak
%       ]
%     insertgraphics qua
%     \vspace{3pt}
%     \hrule
%     \vspace{3pt}
%     \caption{}
% \end{mdframed}\end{figure}

>>>>

% Compilation commands
% lualatex paper.tex
% makeglossaries paper
% biber paper
% lualatex paper.tex

@@

% glossary
\usepackage[acronym, toc]{glossaries}
\makeglossaries
\usepackage[backend=biber, style=ieee]{biblatex}
\addbibresource{references.bib}

@@

% First plot: SSIM and PSNR
\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={SSIM},
        xtick distance={400},
        enlarge x limits=false,
        enlarge y limits=false,
        grid=none,
        thick,
        axis y line*=left,
        axis x line*=bottom,
        legend style={
          at={(0.97,0.16)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      % SSIM on left y-axis
      \addplot[blue, thick] table[x index=0, y index=1] {figures/validation_metrics_ssim.txt};
      \addlegendentry{SSIM}
    \end{axis}

    % Second axis overlay for PSNR
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={PSNR},
        xtick=\empty, % don't duplicate xticks
        yticklabel style={text=red},
        ylabel style={text=red},
        axis y line*=right,
        axis x line=none,
        grid=none,
        thick,
        legend style={
          at={(0.97, 0.03)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      % PSNR on right y-axis
      \addplot[red, thick, dashed] table[x index=0, y index=1] {figures/validation_metrics_psnr.txt};
      \addlegendentry{PSNR}
    \end{axis}
  \end{tikzpicture}

  \caption{Metriche: SSIM (a sinista) e PSNR (a destra) su epochs.}
  \label{fig:ssim_psnr_dual}
\end{figure}

% Second plot: Content loss and Frequency loss
\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
    % Left axis: Content loss
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={Content Loss},
        tick label style={font=\scriptsize},  % Smaller x-axis labels
        xtick distance={400},
        %x tick label style={text width = 1.7cm, align = center, rotate = 70, anchor = north east}, % Optional: rotate for dense x values
        enlarge x limits=false,
        enlarge y limits=false,
        grid=major,
        xmajorgrids=false,
        ymajorgrids=true,
        axis y line*=left,
        axis x line*=bottom,
        legend style={
          at={(0.97,0.97)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      \addplot[green!60!black, thick] table[x index=0, y index=1] {figures/loss_content.txt};
      \addlegendentry{Content Loss}
    \end{axis}

    % Right axis: Frequency loss
    \begin{axis}[
        width=0.9\linewidth,
        ylabel={Frequency Loss},
        yticklabel style={text=orange, font=\scriptsize},
        ylabel style={text=orange},
        xtick=\empty,
        axis y line*=right,
        axis x line=none,
        grid=none,
        enlarge x limits=false,
        enlarge y limits=false,
        legend style={
          at={(0.97,0.84)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      \addplot[orange, thick, dashed] table[x index=0, y index=1] {figures/loss_frequency.txt};
      \addlegendentry{Frequency Loss}
    \end{axis}
  \end{tikzpicture}

  \caption{Training losses nelle epochs: Spatial Loss (a sinistra) and Frequency Loss (a destra).}
  \label{fig:dual_losses}
\end{figure}

@@
